Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
some fine-tuning (adds one line, though)

    %%% CONTEXT %%%
    \begin{itemize}
      \item What is a scientific workflow?
      \item Scientific workflows are all over the place $\rightarrow$ important!
      \item Scheduling (order, maybe even concrete starting times) is important for efficient workflow executions
      \item Only mapping tasks to processors is not enough.
      \item This also allows to reuse processors, which is important to achieve good HW utilization / makespans (explain!).
    \end{itemize}

    %%% MOTIVATION %%%
    \begin{itemize}
      \item Heterogeneous means: different CPU speeds, different mem sizes
      \item With different mem sizes: more difficult to adhere to mem constraints
      \item Adhering to memory constraints is very important to avoid execution failures.
      \item In this paper, we formulate the problem that takes memories into consideration (using (nearly the) model from ICPP paper)
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

>>>>

    %%% CONTEXT %%%
    The analysis of massive datasets, originating from fields such as genomics, 
    remote sensing, or biomedical imaging -- to name just a few -- has become ubiquitous in science;
    this often takes the form of workflows, \iec separate software components chained together
    in some kind of complex pipeline~\cite{DBLP:journals/dbsk/LeserHDEGHKKKKK21}.
    These workflows are usually represented as directed acyclic graphs (DAGs).
    The DAG vertices represent the software components (or, more generally, the workflow \emph{tasks}),
    while the edges model I/O dependencies between the tasks~\cite{adhikari2019survey,liuPacitti}.
    Large workflows with resource-intensive tasks can easily exceed the capabilities of a 
    single computer and are therefore executed on a parallel or distributed platform.
    An efficient execution of the workflows on such platforms requires mapping tasks
    to specific processors; to increase utilization by reusing finished processors,
    one also needs a task schedule (\iec a valid execution order that respects the dependencies)
    and possibly also starting times for the tasks.

    %%% MOTIVATION %%%
    Today's computing platforms are often heterogeneous,

    \begin{itemize}
      \item Heterogeneous means: different CPU speeds, different mem sizes
      \item With different mem sizes: more difficult to adhere to mem constraints
      \item Adhering to memory constraints is very important to avoid execution failures.
      \item In this paper, we formulate the problem that takes memories into consideration (using (nearly the) model from ICPP paper)
      \item Objective: makespan (proxy for total execution time)
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}
